Uncovering Distributed System Bugs\\ during Testing (not Production!) -- draft title

### 2015-08-17 paper.tex
added author names in the paper (its currently in alphabetic order and kinda broken, we should discuss and fix)
Initial description of what live migration does.

\numberofauthors{5} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor Draft\\
       \affaddr{Draft}\\
       \email{Draft}
% 2nd. author
\alignauthor Draft\\
       \affaddr{Draft}\\
       \email{Draft}
% 3rd. author
\alignauthor Draft\\
       \affaddr{Draft}\\
       \email{Draft}
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor Draft\\
       \affaddr{Draft}\\
       \email{Draft}
% 5th. author
\alignauthor Draft\\
       \affaddr{Draft}\\
       \email{Draft}
}

@@

>>>>

\numberofauthors{7} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor Nikolaj Bjorner\\
       \affaddr{Microsoft Research}\\
       \affaddr{Redmond, WA, USA}\\
       \email{nbjorner@microsoft.com}
% 2nd. author
\alignauthor Pantazis Deligiannis\\
       \affaddr{Imperial College London}\\
       \affaddr{London, UK}\\
       \email{p.deligiannis@imperial.ac.uk}
% 3th. author
\alignauthor John Erickson\\
       \affaddr{Microsoft}\\
       \affaddr{Redmond, WA, USA}\\
       \email{jerick@microsoft.com}
% 4th. author
\alignauthor Cheng Huang\\
       \affaddr{Microsoft Research}\\
       \affaddr{Redmond, WA, USA}\\
       \email{cheng.huang@microsoft.com}
\and  % use '\and' if you need 'another row' of author names
% 5rd. author
\alignauthor Matt McCutchen\\
       \affaddr{MIT}\\
       \affaddr{Cambridge, MA, USA}\\
       \email{rmccutch@mit.edu}
% 6th. author
\alignauthor Wolfram Schulte\\
       \affaddr{Microsoft}\\
       \affaddr{Redmond, WA, USA}\\
       \email{schulte@microsoft.com}
% 7th. author
\alignauthor Shaz Qadeer\\
       \affaddr{Microsoft Research}\\
       \affaddr{Redmond, WA, USA}\\
       \email{qadeer@microsoft.com}
}

@@

\subsection{Live Azure Table Migration}

We also used \psharp to test the MigratingTable library, which can be integrated into an application that accesses data using the Windows Azure table storage service and is capable of migrating the data from one underlying Azure table to another, transparent to the application.  MigratingTable provides a ``virtual table'' with an API similar to that of an ordinary Azure table.  Each read and write on the virtual table is translated to a sequence of reads and writes on the underlying tables according to a protocol we designed, which guarantees linearizability of operations on the virtual table across multiple application processes assuming that the underlying tables respect their own linearizability guarantees.

% N.B. Artifact Services is mentioned at http://research.microsoft.com/en-us/people/schulte/.  Hopefully it's OK to reveal that it was the system in this case study. ~ Matt 2015-08-17
The initial motivation for MigratingTable was to solve a scaling problem for Artifact Services, an internal Microsoft system with a data set that is sharded across tables in different Azure storage accounts because of the limit on traffic supported by a single Azure storage account.  As the traffic continues to grow over time, we will need to reshard the data set across a greater number of Azure storage accounts without interrupting service.  During such a resharding, our sharding manager will identify each key range that should migrate to a different table, and we will use a separate MigratingTable instance for each such key range to actually perform the migration.  MigratingTable may also be useful to migrate data to a table with different values of configuration parameters that Azure does not support changing on an existing table, such as geographic location.

Since we were designing a new concurrent protocol that we expected to become increasingly complex over time as we add optimizations, we planned from the beginning to maintain a \psharp test harness along with the protocol to maintain confidence in its correctness.

\subsubsection{Modeling approach}
% TBD where this goes ends up in the paper ~ Matt 2015-08-17

TODO
